Interval Probability for Fuzzy Quantum Theories

### 2016-06-19 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add an exmaple...

Notice that if the last condition is replaced by equal sign, these
conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
Therefore, it is reasonable to believe these conditions should be
equivalent to a interval-valued Born rule.

@@

>>>>

Notice that if the last condition is replaced by the equal sign, these
conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
Therefore, it is reasonable to believe these conditions should be
equivalent to a interval-valued Born rule.

@@

\begin{example}[Totally ignorant quantum interval-valued probability
measure] For any Hilbert space and intervals\emph{~$\mathscr{I}=\left\{ \left[0,0\right],\left[0,1\right],\left[1,1\right]\right\} $},
consider $\mu:\events\rightarrow\mathscr{I}$ defined as follow: 
\[
\mu(E)=\begin{cases}
\left[1,1\right] & \textrm{, if }E=\mathbb{1}\textrm{ ;}\\
\left[0,0\right] & \textrm{, if }E=\mathbb{0}\textrm{ ;}\\
\left[0,1\right] & \textrm{, otherwise.}
\end{cases}
\]
It is easy to verify $\mu$ is a quantum \emph{$\mathscr{I}$}-interval-valued
probability measure.\qed\end{example}
